---
title       : Pitch Presentation
subtitle    : 
author      : Lavanya Rebba
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {stbroandalone, draft}
knit        : slidify::knit2slides
copy_libraries: true
---

## Introduction

 - This is a reproducible pitch presentation about my Shiny application.

 - The presentation was generated using RStudio and Slidify

---

## Application

 - The Shiny Ap 'COURSE9_WEEK4_ASSIGNMENT_SHINYAPP' is up & running at https://lrebba.shinyapps.io/course9_week4_assignment_shinyapp/
 
 - This application shows an example of making a web application
 using R and Shiny framework.
 
 - The data was extracted from the 1974 Motor Trend US magazine, and comprises 
 fuel consumption and 10 aspects of automobile design and performance
 for 32 automobiles (1973-74 models).
 
 - In the application, the relationship between variables and
 miles per gallon (MPG) is determined using box plot and regression model.
 
 - Github Repo is https://github.com/lrebba-git/Developing-Data-Products

---

## Source

The data was extracted from the ***1974 Motor Trend*** US magazine, 
and comprises fuel consumption and 10 aspects of automobile design
and performance for 32 automobiles (1973-74 models).

Next, the dataset structure: 
```{r}
library(shiny)
library(datasets)
head(mtcars, 3)
```

---

## Data Set {.smaller}

| Index | Field | Detail |
------- | ----- | ------ |
| 1     | mpg   | Miles/(US) gallon |
| 2     | cyl   | Number of cylinders |
| 3     | disp  | Displacement (cu.in.) |
| 4	    | hp    | Gross horsepower |
| 5	    | drat  | Rear axle ratio |
| 6     | wt    | Weight (lb/1000) |
| 7	    | qsec  | 1/4 mile time |
| 8	    | vs    | V/S |
| 9	    | am    | Transmission (0 = automatic, 1 = manual) |
| 10    | gear  | Number of forward gears |
| 11    | carb  | Number of carburetors |

---

## Server Code

```{r echo= TRUE}
mpgData <- mtcars
mpgData$am <- factor(mpgData$am, labels = c("Automatic", "Manual"))

 formulaTextPoint <- reactive({
    paste("mpg ~", "as.integer(", input$variable, ")")  })
  
  fit <- reactive({
    lm(as.formula(formulaTextPoint()), data=mpgData)  })
  
  it <- renderPrint({
    summary(fit()) })
  
  mpgPlot <- renderPlot({
    with(mpgData, {
      plot(as.formula(formulaTextPoint()))
      abline(fit(), col=2)
    })  })
  
```





